Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-05-24 manuscript.Rmd
rename vars

```{r message=FALSE, include=FALSE, results='hide'}
library(tidyverse)
library(lme4)
library(lmerTest)
library(rio)
```

@@

# Make variable types/names congruent for merging
# rename
library(magrittr)
ind_diffs_self %<>% 
  rename(PerUn = SubNum)

@@

# select relevant variables
df <- df %>% 
  select(
    PerUn:Group, # id variables
    EA100, # emphatic accuracy (EA) for thoughts out of 100
    sex:race_text, # demographic variables
    strait1:strait26, # perceivers' self-reported personality traits
    imp1:imp16, # rapport during the interaction
    ptrait1:ptrait26, # perception of targets' personality traits
    targSR1:targSR26, # targets' self-reported personality traits
    Self1:Self120, # perceivers' self-reported continuous affect
    Part1:Part120, # perception of targets'continuous affect
    TargSR1:TargSR120, # targets' self-reported continuous affect
    as1:as13, # attachment styles
    auth1:auth12rc, # authenticity
    mask1:mask13, # masking
    ntb1:ntb10, # need to belong
    ucla1:ucla20rc, # ucla loneliness scale
    fne1:fne12, # fear of negative evaluation
    beq1:beq16, # berkeley expressivity questionnaire
    erq1:erq10, # emotion regulation (expressive suppression)
    rse1:rse10rc, # rosenberg self-esteem
    sat1:sat5, # satistaction with life
    pow1:pow8, # sense of power
    sias1:sias12, # social interaction anxiety scale
    InsecAtt:SIAPSc, # composite variables
    InformantTot, # number of informants for targets
    strait4rc:strait25rc, # perceivers' traits reversed and centered
    Extr:Trust, # composite variables for personality traits
    itrait1:itrait26, # informant reports of targets' personality traits
    per_InsecAtt_INFmeanC:per_Trust_INFmeanC # informant reports 
  ) %>% 
  arrange(PerUn, TarUn, DyUn, Group)

# rename variables for a final time
ids <- paste0(c("perceiver", "target", "dyad", "group"), "id")

>>>>

```{r message=FALSE, include=FALSE, results='hide'}
library(tidyverse)
library(lme4)
library(lmerTest)
library(rio)
library(magrittr)
```

@@

# Make variable types/names congruent for merging
# rename
ind_diffs_self %<>% 
  rename(PerUn = SubNum)

@@

# select relevant variables
df <- df %>% 
  select(
    PerUn:Group, # id variables
    EA100, # emphatic accuracy (EA) for thoughts out of 100
    sex:race_text, # demographic variables
    imp1:imp16, # rapport during the interaction
    strait1:strait26, # perceivers' self-reported personality traits
    ptrait1:ptrait26, # perception of targets' personality traits
    targSR1:targSR26, # targets' self-reported personality traits
    Self1:Self120, # perceivers' self-reported continuous affect
    Part1:Part120, # perception of targets'continuous affect
    TargSR1:TargSR120, # targets' self-reported continuous affect
    as1:as13, # attachment styles
    auth1:auth12rc, # authenticity
    mask1:mask13, # masking
    ntb1:ntb10, # need to belong
    ucla1:ucla20rc, # ucla loneliness scale
    fne1:fne12, # fear of negative evaluation
    beq1:beq16, # berkeley expressivity questionnaire
    erq1:erq10, # emotion regulation (expressive suppression)
    rse1:rse10rc, # rosenberg self-esteem
    sat1:sat5, # satistaction with life
    pow1:pow8, # sense of power
    sias1:sias12, # social interaction anxiety scale
    InsecAtt:SIAPSc, # composite variables
    InformantTot, # number of informants for targets
    Extr:Trust, # composite variables for personality traits
    itrait1:itrait26, # informant reports of targets' personality traits
    per_InsecAtt_INFmeanC:per_Trust_INFmeanC # informant reports 
  ) %>% 
  arrange(PerUn, TarUn, DyUn, Group)

# rename variables for a final time
ids <- paste(c("perceiver", "target", "dyad", "group"), "id", sep = "_")
rapport <- paste0("rapport", 1:16)
personality <- map(c("perceiver_trait", "target_trait", "judgment_trait"),
                   ~ paste0(.x, 1:26)) |> unlist()
affect <- map(c("perceiver_affect", "target_affect", "judgment_affect"),
              ~ paste0(.x, 1:120)) |> unlist()
sbw <- paste0("swb", 1:5)
informant <- paste0("informant_trait", 1:26)

df <- df %>% 
  rename_at(vars(c(PerUn:Group, imp1:imp16, strait1:TargSR120, sat1:sat5,
                 itrait1:itrait26)),  ~
            c(ids, rapport, personality, affect, sbw, informant))
